|

### 2021-12-09 text/ManuscriptDraft.Rmd
Updated manuscript

@@

@@

@@

![](../figures/figure_1.png){ width=100% }

**Figure 1:** Simple centroid tracking may produce erronous associations when objects move between frames. Blue shows detections in the current frame (bounding box and centroid point). Red shows centroid points for the detections in the previous frame.

@@

The code that supports the results in this paper will be made openly available at https://github.com/TECOLOGYxyz. Raw data as well as the trained flower detection model will be archived on https://zenodo.org/.

>>>>

![](../figures/figure_1.png){ width=100% }
**Figure 1:** Simple centroid tracking may produce erronous associations when objects move between frames. Blue shows detections in the current frame (bounding box and centroid point). Red shows centroid points for the detections in the previous frame.

@@

![](../figures/figure_22.jpg){ width=100% }

@@

![](../figures/figure_3.png){ width=100% }

@@

@@

The code that supports the results in this paper will be made openly available at https://github.com/TECOLOGYxyz/FlowerTracking. Raw data as well as the trained flower detection model will be archived on https://zenodo.org/.
